\documentclass[../../dissertation.tex]{subfiles}
\begin{document}

This chapter studies the search problem using quantum walks will be presented.
Section \ref{sec:GrovSearchSimul} introduces the basics of a search problem by
presenting the theoretical framework of Grover's algorithm, followed by a
complexity analysis, together with Python plots for a better illustration.
Different numbers of marked elements will be shown and, by the end of the
section, it should be clear that Grover's algorithm is optimal for searching,
as shown by \cite{zalka1999}.\par

Subsequent sections are dedicated for the quantum walk instance of this
problem. In section \ref{sec:CoinedSearchSimul}, the coined quantum walk is
defined for the search problem, which implies the introduction of an oracle.
Here, instead of a line, a complete graph is used, which will increase the
space of the search to $2N$, due to the connected nature of this graph and the
need of a coin. Section \ref{sec:StagSearchSimul} presents the staggered
quantum walk version of the search problem. Again, the notion of cliques and
tessellations is used instead of a coin, and the complete graph is again
considered. The oracle is again defined for this walk, which makes it quite
similar to Grover's algorithm. However, since it is possible to alter the
parameter $\theta$ and the structure over which the search is performed, this
algorithm is known to be more general then Grover's. Like the coined quantum
walk, the staggered model is discrete in time but, since a coin is not used,
the space associated with it scales only with the size of the graph, meaning
its implementation on a NISQ computer will be more feasible. Finally, section
\ref{sec:ContSearchSimul} closes this chapter with the search instance of the
continuous-time quantum walk. Similarly to the staggered quantum walk, both the
structure where the search is performed and parameter $\gamma$ can be
controlled. However, because time is not discrete in this instance, the
probability distribution associated with this walk will be slightly different,
and it will later be seen that this results in a circuit that does not scale up
with time.  


\end{document}
