\documentclass[../../dissertation.tex]{subfiles}

\begin{document}

Chapter \ref{chap:introduction} begins with a brief historical overview of the
origins of quantum computation, starting with the early days of computer
science all the way to quantum walks. An overview of the state of the art
encompassing both theoretical and circuit implementations of quantum walks and
searching problems was presented in a further section, including the relevant
literature to the work presented in this thesis. Thisi introduction is then
closed with an overview of the following chapters and main contributions.\par

The goal of the chapter \ref{chap:QuantumWalks} was to define the theoretical
framework associated with the three quantum walk models studied in this thesis.
This was done in the context of the quantum walk on the line, starting with a
brief definition of the classical random walk, followed by the discrete models
of the quantum walk, namely the coined model and the staggered model, and
finishing with the continuous-time quantum walk. All of the models were
simulated in Python, and variuous plots were created in order to analyse how
the different parameters influence how the dynamics of each walk behave.\par

Chapter \ref{chap:searchingProblems} was dedicated to the study of the
previously defined quantum walks when applied to the searching problem. It
starts with the definition of the Grover algorithm, where a complexity analysis
was performed, followed by the quantum walk analogue. Here, the theoretical
explanation for the various quantum walks on complete graphs was presented,
combined with the introduction of the oracle. Similarly to the previous
chapter, Python was used to simulate the algorithms and study how the different
aspects of each model affect how the the search problem evolves.\par

The main contributions of this thesis are presented in chapter
\ref{chap:qiskitImplementation}. The first contribution comes in the form
of a systematic way of creating Qiskit circuits continuous-time quantum walks
for a myriad of circulant graphs, by way of the quantum Fourier transform and
Qiskits \textit{diagonal} function, presented in the work by \cite{chagassantos21}. Previous work by \cite{qiang2016} uses
the concept of circulant graphs for the implementation of the CTQW model on a
complete graph for a small number of qubits, however the present work provides
a systematic way of generating graphs for a much greater number of circulant
graphs, for an arbitrary number of qubits, as well as an analysis of how the
approximate quantum Fourier transform can be used to reduce circuit depth for
better NISQ computer results. 
%TODO: Grover
Another contribution, that is not found on the
literature, was the use of this method to implement search on circulant graphs
using the continuous-time quantum walk.  The results were not as satisfactory
as the previous dynamics example, because of the the increased circuit size due
to the introduction of the oracle and Suzuki-Trotter iterations. This is still
a work in progress, which will be further expanded upon in future publications.
This chapter also contains a compilation of methods for creating circuits for
the dynamics and search of the discrete-time quantum walk models, based mainly
on the work of \cite{douglaswang07} and \cite{acasiete2020}, which are not
original contributions but hopefully provide a useful overview on how to
implement these algorithms on current quantum hardware.\par

Based on the work presented in this thesis, future work for the study and
implementation of quantum walks includes the following:
\begin{enumerate}
	\item Circuit implementation of the continuous-time quantum walk search problem using circulant graphs, and how the AQFT affects circuit depth and implementability on NISQ computers. This is the goal of the next publication regarding this thesis.
	\item Simulation, implementation and analysis of the searching problem for multiple marked elements using the staggered quantum walk model. The search problem with the SQW is not very well researched in the literature, meaning there are contributions to be made in this regard.
	%TODO: Problemas de transporte??	
	\item Analysis through the creation of simulation software of the continous-time quantum walk from the perspective of transport problems, such as localization, perfect state transfer and mixing time, and further analysis of the search problem for multiple marked elements.
	%TODO: Perspetiva do locke?
	\item Development of a method for constructing staggered quantum walk circuits for a larger variety of graphs.
	\item Expansion of the circulant graph method for the CTQW in order to perform the walk over a larger class of graphs.
\end{enumerate}


\end{document}
