\documentclass[../../dissertation.tex]{subfiles}
\begin{document}

This chapter is dedicated to the construction of quantum walk circuits using
IBMs software, \textit{Qiskit}, whose code is presented in the Github
repository\footnote{https://github.com/JaimePSantos/QWQiskit}. It is composed
of two parts, sections \ref{sec:CoinedQiskit} through \ref{sec:ContQiskit}
present the circuits for the dynamics of each previously studied quantum walk
model and the chapter is closed with section \ref{sec:SearchProblemsQiskit},
where the search problem for each model is implemented.\par 

The first part of this chapter begins with section \ref{sec:CoinedQiskit},
where the coined quantum walk implementation based on the work of
\cite{douglaswang07} can be found. Here, the line graph is again considered,
whose shift operation is composed of increment and decrement gates constructed
with generalized CNOT gates. As was seen in previous chapters, this model
requires an extra qubit for the space of the coin that, when combined with all
the operations required to implement the generalized CNOT gates, results in a
circuit far too deep to be implemented in current NISQ computers, as was
concluded at the end of this section. The staggered quantum walk circuit is
presented in the following section, whose construction was based on the work of
\cite{acasiete2020}. This implementation still uses the notion of the increment
and decrement operations however, since a coin was not required, the resulting
circuit becomes much more NISQ-friendly.The first part is then concluded with
section \ref{sec:ContQiskit}, where the continuous-time quantum walk circuit is
implemented. Here, the best results for the dynamics of the quantum walk were
obtained, due to the circulant graph approach that, unlike the previous
discrete models, does not require extra iterations of the algorithm to
represent time. Work by \cite{qiang2016} firstly presented the circulant graph
definition of this model limited to the complete graph case, and the final part
of this section greatly expands on this work by means of statistical analysis
of the impact of the approximate quantum Fourier transform on a large
collection of circulant graphs.\par

%TODO: Esta parte esta um bocado fraca.
Finally, section \ref{sec:SearchProblemsQiskit} closes this chapter with the
creation of circuits for the search problem using quantum walks. It starts with
the introduction of quantum searching by means of the circuit associated with
Grover's algorithm, followed by the coined quantum walk, which produces the
worst results due to the requirement of $2n$ qubits and swap gates for the
representation of the complete graph. Surprisingly, the best results were
achieved for the staggered quantum walk search problem, since it produced the
circuit with the least operations. The continuous-time quantum walk search was
expected to produce the best results in this section also, but the introduction
of the oracle together with the requirement of the Suzuki-Trotter expansion
resulted in a circuit somewhat impacted by noise.
\end{document}
